Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-07-19 jsm/speed-presentation/slides.tex
minor change

\begin{frame}{Popularity Adjusted Block Models are Generalized Random
Dot Product Graphs}
\protect\hypertarget{popularity-adjusted-block-models-are-generalized-random-dot-product-graphs}{}
Published in \emph{Journal of Computational and Graphical Statistics}

>>>>

\begin{frame}{Thank you}
\protect\hypertarget{thank-you}{}
Published in \emph{Journal of Computational and Graphical Statistics}
